### 2017-07-27 paper/oopsla17-cameraready/evaluation-user-study.tex
rearrange threats per wes+kamalika

We assigned three problems to the students: the |padZero| and
|mulByDigit| programs from \autoref{sec:qualitative}, as well as
the following |sepConcat| program
%
\begin{ecode}
  let rec sepConcat sep sl =
    match sl with
    | [] -> ""
    | h::t ->
        let f a x = a ^ (sep ^ x) in
        let base = (*@\hlTree{[]}@*) in
        (*@\hlSherrloc{List.fold\_left f base sl}@*)
\end{ecode}
%
where the student has erroneously returned the empty list, rather than
the empty string, in the base case of the fold.
% which triggers an error on line 7.
%
% For each problem the students were given the ill-typed program and
% either \ocaml's error or \toolname's jump-compressed trace;
%
The full user study is available in \autoref{sec:user-study-exams}.
%
Due to the nature of an in-class exam, not every student answered every
question, but we always received at least 12 (out of a possible 15 or
16) responses for each problem-tool pair.
%
%A further complication for this study is that
This session of the course
was taught in \textsc{Reason},\footnote{\url{https://reasonml.github.io}}
a dialect of \ocaml with a more C-like syntax, and thus for the study
we transcribed the programs to \textsc{Reason} syntax.

@@

@@

\mypara{Results}
%
The measured kappa values were $\kappa = 0.68$ for the explanations and
$\kappa = 0.77$ for the fixes; while there is no formal notion for what
consititutes strong agreement~\cite{Krippendorff2012-wd}, kappa values
above $0.60$ are often called ``substantial''
agreement~\cite{Landis1977-ey}.
%
Figure~\ref{fig:results-user-study} summarizes a single annotator's
results, which show that students given \toolname's blame assignment
were generally more likely to correctly explain and fix the type error
than those given \sherrloc's.
%
There was no discernible difference between \toolname and
\sherrloc for |sepConcat|; however, \toolname responses for |padZero| and
|mulByDigit| were marked correct 5--25\% more often than the \sherrloc
responses.
%
While the results appear to show a trend in favor of \toolname,
they do not rise to the level of statistical significance;
further investigation is merited.
% The results appear to show a trend in favor of \toolname;
% %
% however, none rise to the level of statistical significance.
%

>>>>

We have demonstrated in the preceding sections that we can produce
more \emph{accurate} blame assignments by learning from the collective
mistakes of prior students; however, users are the final judge of
the \emph{utility} of an error message.
%
Thus, in this final experiment we ask whether \toolname's correct blame
assignments aid users in \emph{understanding} type errors
more than incorrect assignments.

We assigned three problems to the students in our user study: the
|padZero| and |mulByDigit| programs from \autoref{sec:qualitative}, as
well as the following |sepConcat| program
%
\begin{ecode}
  let rec sepConcat sep sl =
    match sl with
    | [] -> ""
    | h::t ->
        let f a x = a ^ (sep ^ x) in
        let base = (*@\hlTree{[]}@*) in
        (*@\hlSherrloc{List.fold\_left f base sl}@*)
\end{ecode}
%
where the student has erroneously returned the empty list, rather than
the empty string, in the base case of the fold.
% which triggers an error on line 7.
%
For each problem the students were additionally given either \toolname's
correct blame assignment or \sherrloc's incorrect blame assignment,
with no error message.
% For each problem the students were given the ill-typed program and
% either \ocaml's error or \toolname's jump-compressed trace;
%
The full user study is available in \autoref{sec:user-study-exams}.
%
Due to the nature of an in-class exam, not every student answered every
question, but we always received at least 12 (out of a possible 15 or
16) responses for each problem-tool pair.
%
%A further complication for this study is that
This session of the course
was taught in \textsc{Reason},\footnote{\url{https://reasonml.github.io}}
a dialect of \ocaml with a more C-like syntax, and thus for the study
we transcribed the programs to \textsc{Reason} syntax.

@@

\mypara{Results}
%
The measured kappa values were $\kappa = 0.68$ for the explanations and
$\kappa = 0.77$ for the fixes; while there is no formal notion for what
consititutes strong agreement~\cite{Krippendorff2012-wd}, kappa values
above $0.60$ are often called ``substantial''
agreement~\cite{Landis1977-ey}.
%
Figure~\ref{fig:results-user-study} summarizes a single annotator's
results, which show that students given \toolname's blame assignment
were generally more likely to correctly explain and fix the type error
than those given \sherrloc's.
%
There was no discernible difference between \toolname and
\sherrloc for |sepConcat|; however, \toolname responses for |padZero| and
|mulByDigit| were marked correct 5--25\% more often than the \sherrloc
responses.
%
While the results appear to show a trend in favor of \toolname,
they do not rise to the level of statistical significance
in this experiment; further investigation is merited.
% The results appear to show a trend in favor of \toolname;
% %
% however, none rise to the level of statistical significance.
%

@@

### 2017-07-27 paper/oopsla17-cameraready/threats.tex
rearrange threats per wes+kamalika

Although our experiments demonstrate that our technique can pinpoint type
errors more accurately than the state of the art and that our features are
relevant to blame assignment, our results may not generalize.

>>>>

Although our experiments demonstrate that our technique can pinpoint type
errors more accurately than the state of the art and that our features are
relevant to blame assignment, our results may not generalize
to other problem domains or program sets.
